Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-03-26 ms/ms08_figures.tex
ENH

\begin{figure}[!tbp]

    \begin{subfigure}[]{.24\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_perc_tophits_eqtl.py/autoimmune_disease.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.24\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_perc_tophits_eqtl.py/cardiovascular_disease.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.24\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_perc_tophits_eqtl.py/digestive_system_disease.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.24\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_perc_tophits_eqtl.py/mental_or_behavioural_disorder.png}
    \end{subfigure}

    \begin{subfigure}[]{\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    \end{subfigure}

>>>>

\begin{figure}[!tbp]
    \centering

    \begin{subfigure}[]{\textwidth}
        \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    \end{subfigure}
